# Reproducible Research: Peer Assessment 1


## Loading data and transform the date in the data to Date type
```{r}
data <- read.csv("activity.csv")
data$date <- as.factor(data$date)
data$interval <- as.factor(data$interval)
str(data)
```
As we can see, the data contain 3 varibles which are numeric variables "steps", date variable "date" (converted to factors) and numerical variable "interval" (converted to factors).  


## What is mean total number of steps taken per day?
```{r}
library("ggplot2")
stepsDaySum <- data.frame (stepSums = rep(0,length(levels(data$date))), day = "2000-1-1", stringsAsFactors = FALSE)
for (i in 1:length(levels(data$date))){
  stepsDaySum$stepSums[i] <- sum(subset(data$steps, data$date == levels(data$date)[i]), na.rm = TRUE)
  stepsDaySum$day[i] <- levels(data$date)[i]
}
qplot(stepSums, data = stepsDaySum)
meanStepsSumDay <- mean(stepsDaySum$stepSums, na.rm = TRUE)
medianStepsSumDay <- median(stepsDaySum$stepSums, na.rm = TRUE)
```
The mean of the steps in every day is about 
```{r}
meanStepsSumDay
```
The median of the steps in every day is about 
```{r}
medianStepsSumDay

```




## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
